---
title: "lab 8"
author: "Hollie Pennington"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning + FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
#attach packages
library(here)
library(tidyverse)
library(corrplot)
library(stargazer)
library(modelsummary)
library(broom)
```

```{r}
#read in data 

homes <- read_csv(here("data", "slo_homes.csv"))
```

A little bit of cleaning: 

Make a subset called homes_sub that only contians observations (rows) where the city is: 

- San Luis Obispo 
- Arroyo Grande 
- Atascadero 
- Santa Maria-Orcutt 

```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt")) 
``` 

## Do a little exploring of our data 

Summary statistics (home price, based on city and sale status)
- find and return in nice summary table the mean and standard deviation of price, grouped by city and sale status. 

```{r, include = FALSE, eval = FALSE}
homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE), 
            sd_price = sd(Price, na.rm = TRUE))

#Actually I don't want to run this code: eval = FALSE 

ggplot(data = homes_sub, aes(x = Price)) + 
  geom_density(aes(color = City, fill = City), alpha = 0.3) + 
  scale_x_continuous(limits = c(0, 3e6))

#alpha makes it transparent - alpha is not in aes because it is not referring to a variable 
#3e6 is 3 million, the e is an exponent 
```

Explore the relationship (visual data exploration) between square footage and home price. Change the point COLOR by City, and the point shape by sale status. 

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price)) + 
  geom_point(aes(color = City, shape = Status)) + 
  geom_smooth(method = "lm")
```

## Model the relationship with home price as DV

```{r}
homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub)
homes_lm1

#Make a subset that only contains the quantitative variables 

homes_quant <- homes_sub %>% 
  select(Price:PricePerSqFt) 

homes_cor <- cor (homes_quant)
homes_cor

corrplot(homes_cor)
plot(homes_lm1)
```

Try another model (homes_lm2) where we simplify this a bit: 

- City 
- SqFt 
- Status 

```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, data = homes_sub)

homes_lm2

plot(homes_lm2)
```


Find the AIC value of each model:

```{r}
AIC(homes_lm1)
AIC(homes_lm2)
```
Lower AIC show a better fit. 


Try another permutation of this model that you think might make sense, check out and compare the model fit, outputs and AIC value. 

```{r}
homes_lm3 <- lm(Price ~ Bedrooms + Bathrooms + SqFt + Status + City, data = homes_sub)

summary(homes_lm3)
homes_lm3
```

```{r}
AIC(homes_lm1)
AIC(homes_lm2)
AIC(homes_lm3)
```

Use 'modelsummary' to show model outputs side-by-side: 

If you use modelsummary to return model outputs of multiple models, it wants you to feed it to it as a list. 

```{r}
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

## Start making predictions with these model 

Use `broom::augment()` 

```{r}
homes_predicted <- augment(homes_lm1)
```

Use the `predict()` function 