---
title: "lab 8"
author: "Hollie Pennington"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning + FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
#attach packages
library(here)
library(tidyverse)
library(corrplot)
library(stargazer)
library(modelsummary)
```

```{r}
#read in data 

homes <- read_csv(here("data", "slo_homes.csv"))
```

A little bit of cleaning: 

Make a subset called homes_sub that only contians observations (rows) where the city is: 

- San Luis Obispo 
- Arroyo Grande 
- Atascadero 
- Santa Maria-Orcutt 

```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt")) 
``` 

## Do a little exploring of our data 

Summary statistics (home price, based on city and sale status)
- find and return in nice summary table the mean and standard deviation of price, grouped by city and sale status. 

```{r, include = FALSE, eval = FALSE}
homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE), 
            sd_price = sd(Price, na.rm = TRUE))

#Actually I don't want to run this code: eval = FALSE 

ggplot(data = homes_sub, aes(x = Price)) + 
  geom_density(aes(color = City, fill = City), alpha = 0.3) + 
  scale_x_continuous(limits = c(0, 3e6))

#alpha makes it transparent - alpha is not in aes because it is not referring to a variable 
#3e6 is 3 million, the e is an exponent 
```

